---
title: "Pilot Analysis_Exp5"
author: "Mrudula"
date: "1/12/2021"
output: html_document
---

This is the data analysis  for Experiment 5 with a visual search display and manipulating saliency using the position of the target number on the salient/non salient distractor

```{r include=FALSE}
library(tidyverse)
library(plyr)
library(ez)
library(schoRsch)
library(knitr)
library(pander)
library(rmarkdown)
library(lme4)
library(reshape2)
library(Hmisc)

library(here)
#set_here()

#p1 <- read.csv(here("Data","Pilot_hiwi","pilot1.csv"))
p2 <- read.csv(here("Data","Pilot_hiwi","pilot2.csv"))
p3 <- read.csv(here("Data","Pilot_hiwi","pilot3.csv"))
p4 <- read.csv(here("Data","Pilot_hiwi","pilot4.csv"))
p5 <- read.csv(here("Data","Pilot_hiwi","pilot5.csv"))

pilotdata <- rbind.fill(p2,p3,p4,p5)




```

Removing unnecessary columns 

```{r datacleaning, include=FALSE}
pilotdata <- pilotdata %>%
  select(-ConsentKey.keys,-ConsentKey.rt,-Begin.keys,-Begin.rt,-checkresp.corr,-checkresp.keys,-checkresp.rt,-Attention.thisRepN,-Attention.thisTrialN,-Attention.thisN,-Attention.thisIndex,-Attention.ran,-AttnQuestion,-AttnAnswer,-NextStep.keys,-NextStep.rt,-InstRep.ran,-InstRep.thisTrialN,-InstRep.thisRepN,-InstRep.thisIndex,-PracProceed.keys,-PracProceed.rt,-Prac_loop.thisRepN,-Prac_loop.thisTrialN,-Prac_loop.thisN,-Prac_loop.thisIndex,-Prac_loop.ran,-Exp_proceed.keys,-Exp_proceed.rt,-PracRepeat.ran,-PracRepeat.thisRepN,-PracRepeat.thisN,-PracRepeat.thisIndex,-PracRepeat.thisTrialN,-brkContinue.keys,-PauseResp.keys,-PauseResp.rt,-blocks.thisRepN,-blocks.thisTrialN,-blocks.thisIndex,-blocks.ran,-CA_Proceed.keys,-CA_Proceed.rt)

pilotdata <- pilotdata %>%
  select(-InstRep.thisN)

pilotdata <- pilotdata%>%group_by(participant)%>%fill(Screen_bg,.direction = "down")

pilotdata <- pilotdata %>% group_by(participant)%>%fill(blocks.thisN,.direction = "up")

#adjusting RT
pilotdata <- separate(pilotdata, col = TargetResp.rt, into = c("RT_Trials", "RT_secondary"), sep = ',')
pilotdata$RT_Trials <- pilotdata$RT_Trials%>%
  str_replace_all("\\[|\\]","")%>%
  as.double(pilotdata$RT_Trials)
pilotdata$RT_Trials <- 1000*(pilotdata$RT_Trials)

###creating a separate df with the contingency awareness
Exp5pilot_CA <- pilotdata%>%
 filter(Block == "ContingencyCheck" | str_detect(AwareQ, "response"))
pilotdata <- pilotdata%>%drop_na(RT_Trials)

pilotdata$ACC_trials <- pilotdata$TargetResp.corr
pilotdata$ErrorRate <- 1 - pilotdata$ACC_trials

pilotdata <- pilotdata %>%
  select(-headstartLearn.thisRepN,-headstartLearn.thisTrialN,-headstartLearn.thisIndex,-headstartLearn.thisN,-headstartLearn.ran,-ExpTrials.ran,-ExpTrials.thisIndex,-CA_trials.thisRepN,-CA_trials.thisN,-CA_trials.thisIndex,-CA_trials.thisTrialN,-CA_trials.ran,-AwareQ_loop.thisRepN,-AwareQ_loop.ran,-AwareQ_loop.thisIndex,-AwareQ_loop.thisN,-AwareQ_loop.thisTrialN,-todebrief.keys,-Finalend.keys)

```

Descriptives

```{r}
pander(summary(pilotdata$RT_Trials), style = 'rmarkdown',caption = 'Mean RT')
pander(table(pilotdata$ACC_trials),style = 'rmarkdown',caption = "Accuracy")

pander(round(table(pilotdata$ACC_trials)/nrow(pilotdata)*100, digits = 3), style = 'rmarkdown', caption = "Percentage of errors")
```
Exclusion of outliers and farouts

```{r exclusions, echo=FALSE}

pilotdata$RT_Trials[pilotdata$ACC_trials==0] <- NA


#creating function to remove the outliers and farouts
computeTukeys <- function(x){
  P25 <- quantile(x$RT_Trials, .25, na.rm = TRUE, type = 6) #type = 6 -> used in SPSS
  P75 <- quantile(x$RT_Trials, .75, na.rm = TRUE, type = 6)
  x$Outlier <- P75 + 1.5*(P75 - P25)
  x$Farouts <- P75 + 3.0*(P75 - P25)
  return(x)
}


#identifying the outliers and farouts at individual level
pilotdata <- ddply(pilotdata, .(participant), computeTukeys)

#creating new column with RT trials after removing outliers/farouts
pilotdata$RT_ifo <- pilotdata$RT_Trials
pilotdata$RT_io <- pilotdata$RT_Trials
sum(is.na(pilotdata$RT_Trials))
pilotdata$RT_ifo[pilotdata$RT_ifo > pilotdata$Farouts|pilotdata$RT_ifo < 300] <- NA
sum(is.na(pilotdata$RT_ifo))
pilotdata$RT_io[pilotdata$RT_io > pilotdata$Outlier|pilotdata$RT_io < 300] <- NA
sum(is.na(pilotdata$RT_io))

pander(summary(pilotdata$RT_ifo), style = 'rmarkdown', caption = "Summary of RT after removing Farouts")
pander(summary(pilotdata$RT_io), style = 'rmarkdown', caption = "Summary of RT after removing Outliers")

```
Standard Analysis

1. Validity effect 

```{r warning=FALSE, message=FALSE}
pilot5agg_validity <- aggregate(data = pilotdata,RT_ifo~participant+Validity,mean)


anova_V_agg <- ezANOVA(data = pilot5agg_validity,
        dv = RT_ifo,
        wid = participant,
        within = .(Validity),
        detailed = TRUE)
panderOptions('table.split.table',300)
pander(anova_V_agg, style = "rmarkdown", caption = "ANOVa table for all trials with validity and condition as factors",split.table = Inf, missing = NA)

ezPlot(data = pilot5agg_validity,
        dv = RT_ifo,
        wid = participant,
        within = .(Validity),
       x = Validity, do_bars = FALSE)+
  theme_classic()+
  ggtitle("Mean RT per condition for valid and invalid trials")
```


2. Validity x Saliency interaction

```{r warning=FALSE, message=FALSE}
#aggregate
Exp5pilot_VS_agg_fo <- aggregate(data = pilotdata,RT_ifo~participant+Validity+PosMatch,mean)

#anova
anova_VS_fo <- ezANOVA(data = Exp5pilot_VS_agg_fo,
        dv = RT_ifo,
        wid = participant,
        within = .(PosMatch,Validity),
        detailed = TRUE)

pander(anova_VS_fo, style = 'rmarkdown', caption = "ANOVA results: Farouts excluded for test trials",split.table = "Inf", missing = NA)


ezPlot(data = Exp5pilot_VS_agg_fo,
        dv = RT_ifo,
        wid = participant,
        within = .(PosMatch,Validity),
        split = Validity, x=PosMatch, levels =  list(PosMatch = list(new_order = c('Salient', 'NonSalient'))), do_bars = FALSE)+
        theme_classic()+
        ggtitle("Mean RT for valid and \n invalid trials across saliency")
```
Outliers

```{r warning=FALSE, message=FALSE}
#aggregate
Exp5pilot_VS_agg_o <- aggregate(data = pilotdata,RT_io~participant+Validity+PosMatch,mean)

#anova
anova_VS_o <- ezANOVA(data = Exp5pilot_VS_agg_o,
        dv = RT_io,
        wid = participant,
        within = .(PosMatch,Validity),
        detailed = TRUE)

pander(anova_VS_o, style = 'rmarkdown', caption = "ANOVA results: Farouts excluded for test trials",split.table = "Inf", missing = NA)


ezPlot(data = Exp5pilot_VS_agg_o,
        dv = RT_io,
        wid = participant,
        within = .(PosMatch,Validity),
        split = Validity, x=PosMatch, levels =  list(PosMatch = list(new_order = c('Salient', 'NonSalient'))), do_bars = FALSE)+
        theme_classic()+ylim(700,1200)+
        ggtitle("Mean RT for valid and \n invalid trials across saliency")


```
Finding the mean difference between valid and invalid trials across participants

```{r echo=FALSE, warning=FALSE}
Exp5pilot_agg_fo_wide <- dcast(data = Exp5pilot_VS_agg_fo, participant~Validity+PosMatch, value.var =  "RT_ifo")

Exp5pilot_agg_fo_wide$ValEffect_Salient <- Exp5pilot_agg_fo_wide$invalid_Salient- Exp5pilot_agg_fo_wide$valid_Salient

Exp5pilot_agg_fo_wide$ValEffect_NonSalient <- Exp5pilot_agg_fo_wide$invalid_NonSalient- Exp5pilot_agg_fo_wide$valid_NonSalient

Exp5pilot_agg_fo_wide$participant <- as.factor(Exp5pilot_agg_fo_wide$participant)
m1 <- ggplot(Exp5pilot_agg_fo_wide, aes(x=participant, y = ValEffect_Salient, fill = participant))+
  geom_bar(stat = "identity")+theme_classic()+scale_fill_brewer(palette = "Dark2")
m1
m2 <- ggplot(Exp5pilot_agg_fo_wide, aes(x=participant, y = ValEffect_NonSalient, fill = participant))+
  geom_bar(stat = "identity")+theme_classic()+scale_fill_brewer(palette = "Dark2")
m2


library(ggpubr)
m <- ggarrange(m1,m2,ncol=2)
m
```

